---
title: "HW3"
author: "Federico Chung"
date: "4/7/2021"
output: html_document
---

```{r}
# SEE modeldata package for new datasets
library(tidyverse)         # for graphing and data cleaning
library(tidymodels)        # for modeling
library(stacks)            # for stacking models
library(naniar)            # for examining missing values (NAs)
library(lubridate)         # for date manipulation
library(moderndive)        # for King County housing data
library(DALEX)             # for model interpretation  
library(DALEXtra)          # for extension of DALEX
library(patchwork)         # for combining plots nicely
library(dbplyr)            # for SQL query "cheating" - part of tidyverse but needs to be loaded separately

library(mdsr)              # for accessing some databases - goes with Modern Data Science with R textbook
library(RMySQL)            # for accessing MySQL databases
library(RSQLite)           # for accessing SQLite databases

#mapping
library(maps)              # for built-in maps
library(sf)                # for making maps using geom_sf
library(ggthemes)          # Lisa added - I like theme_map() for maps :)

#tidytext

library(tidytext)          # for text analysis, the tidy way!
library(textdata)          
library(reshape2)
library(wordcloud)         # for wordcloud
library(stopwords)

theme_set(theme_minimal()) # Lisa's favorite theme
```
```{r}
data("house_prices")

# Create log_price and drop price variable
house_prices <- house_prices %>% 
  mutate(log_price = log(price, base = 10)) %>% 
  # make all integers numeric ... fixes prediction problem
  mutate(across(where(is.integer), as.numeric)) %>% 
  select(-price)
```



#SQL


```{r}
con_air <- dbConnect(RMySQL::MySQL(), 
                     dbname = "airlines", 
                     host = "mdsr.cdc7tgkkqd0n.us-east-1.rds.amazonaws.com", 
                     user = "mdsr_public", 
                     password = "ImhsmflMDSwR")
```

```{r}
con_air <- dbConnect_scidb("airlines")
```


```{r}
dbListTables(con_air)
```
```{sql connection=con_air}
SHOW TABLES;
```
```{r}
dbListFields(con_air, "flights")
```

```{sql connection=con_air}
DESCRIBE flights
```

```{sql connection=con_air}
DESCRIBE airports
```


Create a SQL chunk and an equivalent R code chunk that does the following: for each airport (with its name, not code), year, and month find the total number of departing flights, the distinct destinations to which they flew, the average length of the flight, the average distance of the flight, and the proportion of flights that arrived more than 20 minutes late. In the R code chunk, write this out to a dataset. (HINT: 1. start small! 2. you may want to do the R part first and use it to “cheat” into the SQL code).

```{r}
flights<-
  tbl(con_air,
      sql("
          SELECT *
          FROM flights
          "))

airports<-
  tbl(con_air,
      sql("
          SELECT *
          FROM airports
          "))


airports
```




```{r}
flights
```

Join by origin 


```{r}
small_flights<- flights%>%head(200)
small_flights

airports

small_flights%>%
  inner_join(airports, by=c("origin" = "faa"))%>%
  group_by(year, month, name)%>%
  mutate(arr_delay = ifelse(arr_delay>20,1,0))%>%
  summarize(count = n(), distinct_destinations = n_distinct(dest), avg_length = mean(air_time), avg_dist = mean(distance),prop_late = sum(arr_delay)/n())
```
```{sql connection=con_air}
SELECT 
  a.name,
  year,
  month,
  num_flights,
  num_dest,
  avg_air_time,
  avg_dist,
  late_over20
FROM(SELECT 
  year, 
  month,
  origin,
  COUNT(*) AS num_flights,
  COUNT(DISTINCT dest) AS num_dest,
  AVG(air_time) AS avg_air_time,
  AVG(distance) AS avg_dist,
  AVG(arr_delay > 20) AS late_over20
FROM (SELECT * FROM flights LIMIT 10000) fl
GROUP BY origin, month, year) smry
INNER JOIN airports AS a ON (smry.origin = a.faa)
```






